---
title: "Proposal"
author: "Group Green"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(skimr)
library(codebook)
```

```{r load-data, eval=TRUE}
stroke <- read_csv("healthcare_dataset_stroke_data.csv")
```

### Section 1: Introduction  
Our group chose to use the "Stroke Prediction" dataset (https://www.kaggle.com/fedesoriano/stroke-prediction-dataset) from user fedsoriano on Kaggle, to answer our research questions, which are "Which variables are most useful for determining whether an individual is likely to have a stroke?"

The set observes 12 stroke-related factors for 5110 individuals, including id, gender, age, hypertension, heart disease, marriage status, work type, residence type, average glucose level, bmi, smoking status, and whether or not the individual had a stroke. 

### Section 2: Data  
```{r load-data, eval=TRUE}
stroke <- read_csv("healthcare_dataset_stroke_data.csv")
```

```{r, eval=TRUE}
save(stroke,file="./stroke.RData")
```

## Stroke Dataset Codebook
```{r, eval=TRUE}
codebook(stroke)
```

## Skim Stroke Dataset Summary
```{r, eval=TRUE}
skim(stroke)
```

### Section 3: Data Analysis Plan  
*Explanatory variables:*  gender, age, heart disease, bmi, hypertension
*Response variable:* stroke

```{r}
summary(stroke)
```
```{r}
stroke %>%
  ggplot(aes(x=age, y= stroke)) +
  geom_point()+
  geom_smooth()
```

As individuals grow older the predicted model shows that they are more likely to be subject to strokes.

```{r}
stroke %>%
  ggplot(aes(x= avg_glucose_level, y= stroke)) +
  geom_point()+
  geom_smooth()
```
As the average glucose level of an individual increases, the model predicts a higher vulnerability to strokes.

We hope to create some visual representation of the correlation between stroke and each one of the explanatory variables in order to determine which one has the greatest effect on death outcome. Specifically, we plan to create a dot plot or line graph and calculate the correlation coefficient between each of the variables and stroke outcome. However, we are currently searching for a better way to represent the data visually given that the stroke outcome is a boolean value and a dot plot/line graph may not be the best way to illustrate this.




