---
title: "Predicting stroke probability"
subtitle: 
author: "Team Green <br> Matthew Leblanc, Sarika Rau, Martin Zakoian, Josias Zongo"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(showtext)
library(pROC)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r load-data, include=FALSE}
# Load your data here
stroke <- read_csv("../data/healthcare_dataset_stroke_data.csv")
```

```{r factor, include=FALSE}
stroke <- na.omit(stroke)
stroke$gender <- factor(stroke$gender)
stroke$stroke <- factor(stroke$stroke)
```

```{r splitdata, include=FALSE}
set.seed(1234)
stroke_split <- initial_split(stroke, prop = 0.75)
train_data <- training(stroke_split) 
test_data <- testing(stroke_split)
```

```{r modelprelim, include=FALSE}
stroke_model_prelim <- glm(stroke ~ gender + age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_prelim)
```

```{r modelupdated, include=FALSE}
stroke_model_updated <- glm(stroke ~ age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_updated)
```

```{r include=FALSE}
stroke_model_updated2 <- logistic_reg() %>%
  set_engine("glm")
```

```{r samplepred, include=FALSE}
predict(stroke_model_updated, newdata=data.frame(age=30, avg_glucose_level=130, hypertension=0, heart_disease=1), type="response")
```

```{r recipe, include=FALSE}
stroke_rec <- recipe(stroke ~ age + avg_glucose_level + hypertension + heart_disease, data = train_data)
```

```{r workflow, include=FALSE}
stroke_flow <- workflow() %>%
  add_model(stroke_model_updated2) %>%
  add_recipe(stroke_rec)
```

```{r crossval, include=FALSE}
set.seed(3456)
stroke_folds <- vfold_cv(train_data, v = 5)

stroke_fit_rs_1 <- stroke_flow %>%
  fit_resamples(stroke_folds)

collect_metrics(stroke_fit_rs_1, summarize=TRUE)
```

```{r fit, include=FALSE}
test_prob = predict(stroke_model_updated, newdata = test_data, type = "response")
test_roc = roc(test_data$stroke ~ test_prob, plot = TRUE, print.auc = TRUE)
```


class: center, middle

## Which variables are most useful for determining whether an individual is likely to have a stroke? <br> <br> How can we train a model on these variables to predict stroke likelihood?

---
# The dataset

.pull-left[
9 categorical variables:
- id
- gender
- hypertension
- heart disease
- ever married
- work type
- residence type
- smoking status
- stroke
]
.pull-right[
3 quantitative variables:
- age
- average glucose level
- bmi
]

---
# Choosing potential predictor variables

We used a logistical regression model to narrow down predictor variables by their p-values from the following:
- gender
- hypertension
- heart disease
- age
- average glucose level
---
# Choosing potential predictor variables

```{r modelprelim1}
stroke_model_prelim <- glm(stroke ~ gender + age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_prelim)
```
---

class: middle, center

# Why a logistical model?

---
# Creating the model

- eliminated predictor variables with a high p-value, including gender
- trained updated model on training data

---

# Evaluating the model: training data

```{r crossval1, echo=FALSE}
set.seed(3456)
stroke_folds <- vfold_cv(train_data, v = 5)

stroke_fit_rs_1 <- stroke_flow %>%
  fit_resamples(stroke_folds)

collect_metrics(stroke_fit_rs_1, summarize=TRUE)
```

---

# Evaluating the model: training data
```{r fit1, echo=FALSE}
train_prob = predict(stroke_model_updated, newdata = train_data, type = "response")
test_roc1 = roc(train_data$stroke ~ train_prob, plot = TRUE, print.auc = TRUE)
```

---

# Evaluating the model: testing data

```{r fit2, echo=FALSE}
test_prob = predict(stroke_model_updated, newdata = test_data, type = "response")
test_roc = roc(test_data$stroke ~ test_prob, plot = TRUE, print.auc = TRUE)
```

---

class: middle, center

# How can we use this in the real world?
---

# Sample prediction

```{r samplepred1}
predict(stroke_model_updated, newdata=data.frame(age=30, avg_glucose_level=130, hypertension=0, heart_disease=1), type="response")
```

---

class: inverse, middle, center

# Thank you