---
title: "Predicting stroke probability"
subtitle: 
author: "Team Green <br> Matthew Leblanc, Sarika Rau, Martin Zakoian, Josias Zongo"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    lib_dir: libs
    nature:
      ratio: "16:9"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(xaringanthemer)
library(showtext)
library(pROC)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_mono_accent(
  base_color = "#1c5253",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono")
)
```

```{r load-data, include=FALSE}
# Load your data here
stroke <- read_csv("../data/healthcare_dataset_stroke_data.csv")
```

```{r factor, include=FALSE}
stroke <- na.omit(stroke)
stroke$gender <- factor(stroke$gender)
stroke$stroke <- factor(stroke$stroke)
```

```{r splitdata, include=FALSE}
set.seed(1234)
stroke_split <- initial_split(stroke, prop = 0.75)
train_data <- training(stroke_split) 
test_data <- testing(stroke_split)
```

```{r modelprelim, include=FALSE}
stroke_model_prelim <- glm(stroke ~ gender + age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_prelim)
```

```{r modelupdated, include=FALSE}
stroke_model_updated <- glm(stroke ~ age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_updated)
```

```{r include=FALSE}
stroke_model_updated2 <- logistic_reg() %>%
  set_engine("glm")
```

```{r samplepred, include=FALSE}
predict(stroke_model_updated, newdata=data.frame(age=30, avg_glucose_level=130, hypertension=0, heart_disease=1), type="response")
```

```{r recipe, include=FALSE}
stroke_rec <- recipe(stroke ~ age + avg_glucose_level + hypertension + heart_disease, data = train_data)
```

```{r workflow, include=FALSE}
stroke_flow <- workflow() %>%
  add_model(stroke_model_updated2) %>%
  add_recipe(stroke_rec)
```

```{r crossval, include=FALSE}
set.seed(3456)
stroke_folds <- vfold_cv(train_data, v = 5)

stroke_fit_rs_1 <- stroke_flow %>%
  fit_resamples(stroke_folds)

collect_metrics(stroke_fit_rs_1, summarize=TRUE)
```

```{r fit, include=FALSE}
test_prob = predict(stroke_model_updated, newdata = test_data, type = "response")
test_roc = roc(test_data$stroke ~ test_prob, plot = TRUE, print.auc = TRUE)
```


class: center, middle

## Which variables are most useful for determining whether an individual is likely to have a stroke? <br> <br> How can we train a model on these variables to predict stroke likelihood?

---
# The dataset

.pull-left[
9 categorical variables:
- id
- gender
- hypertension
- heart disease
- ever married
- work type
- residence type
- smoking status
- stroke
]
.pull-right[
3 quantitative variables:
- age
- average glucose level
- bmi
]

---
# Choosing potential predictor variables

We used a logistical regression model to narrow down predictor variables by their p-values from the following:
- gender
- hypertension
- heart disease
- age
- average glucose level
---
# Choosing potential predictor variables

```{r modelprelim1}
stroke_model_prelim <- glm(stroke ~ gender + age + avg_glucose_level + hypertension + heart_disease, data = train_data, family = binomial)
summary(stroke_model_prelim)
```
---

class: middle, center

# Why a logistical model?

---
# Creating the model

- eliminated predictor variables with a high p-value, including gender
- trained updated model on training data

---

# Evaluating the model

Training data:

```{r crossval1, echo=FALSE}
set.seed(3456)
stroke_folds <- vfold_cv(train_data, v = 5)

stroke_fit_rs_1 <- stroke_flow %>%
  fit_resamples(stroke_folds)

collect_metrics(stroke_fit_rs_1, summarize=TRUE)
```

---

# Evaluating the model
```{r fit1, echo=FALSE}
train_prob = predict(stroke_model_updated, newdata = train_data, type = "response")
test_roc1 = roc(train_data$stroke ~ train_prob, plot = TRUE, print.auc = TRUE)
```

---

# Evaluating the model

Testing data:

```{r fit2, echo=FALSE}
test_prob = predict(stroke_model_updated, newdata = test_data, type = "response")
test_roc = roc(test_data$stroke ~ test_prob, plot = TRUE, print.auc = TRUE)
```

---

class: middle, center

# How can we use this in the real world?
---

# Sample prediction

```{r samplepred1}
predict(stroke_model_updated, newdata=data.frame(age=30, avg_glucose_level=130, hypertension=0, heart_disease=1), type="response")
```

---

class: inverse, middle, center

# Thank you
---

class: inverse, center, middle

# Section title

---

# Hello World

- Click the `Knit` button to compile your presentation

- Make sure to commit and push all resulting files to your GitHub repo

---

class: inverse, middle, center

# Using xaringan

---

# xaringan

- The presentation is created using the `xaringan` package

- Use `---` to separate slides and `--` for incremental builds

--

- Like this

---

# Layouts

You can use plain text

- or bullet points

.pull-left[
or text in two columns $^*$
]
.pull-right[
- like
- this
]

.footnote[
[*] And add footnotes
]

---

# Code

```{r boring-regression}
# a boring regression
model <- lm(dist ~ speed, data = cars)
tidy(model)
glance(model)
```

---

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

---

## Plot and text

.pull-left[
- Some text
- goes here
]
.pull-right[
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
]

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

---

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

---

background-image: url(https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80)

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# Feeling adventurous?

- Want to find out more about `xaringan`? See https://slides.yihui.name/xaringan/#1.

- You are welcomed to use the default styling of the slides. In fact, that's what I expect majority of you will do. You will differentiate yourself with the content of your presentation.

- But some of you might want to play around with slide styling. The 
`xaringanthemer` provides some solutions for this that: https://pkg.garrickadenbuie.com/xaringanthemer.

- And if you want more bells and whistles, there is also `xaringanExtra`: https://pkg.garrickadenbuie.com/xaringanExtra.
